Approximately Exact Calculations for Linear Mixed Models

### 2015-09-21 ms.tex
repositioned Algorithm 1
various
minor

\renewcommand\thesection{\arabic{section}}
\usepackage{xspace}
\newcommand{\textcompute}{\textsf}
\newcommand{\N}{\text{N}} % Normal 
\newcommand{\R}{\textcompute{R}\xspace}
\newcommand{\IG}{\text{InvGam}}
\newcommand{\RL}{f}
\newcommand{\RLorig}{\text{RL}}
\newcommand{\logRL}{\log\RL}
\newcommand{\logRLorig}{\log\RLorig}
\newcommand{\sigssq}{\sigma_s^2}
\newcommand{\sigesq}{\sigma_e^2}
\newcommand{\sshat}{\hat\sigma^2_e,\hat\sigma^2_s}
\newcommand{\logRLss}{\logRL(\sigesq,\sigssq)}
\newcommand{\logRLssorig}{\logRLorig(\sigesq,\sigssq)}
\newcommand{\ass}{a_j\sigssq + \sigesq}
\newcommand{\abss}{a_j\sigssq + b_j\sigesq}
\newcommand{\fss}{f(\sigesq,\sigssq)\,}
%\newcommand{\mrle}{MRLE}
\newcommand{\mrle}{$\argsup\log f$}
%\newcommand{\lone}{\textbf{l}_1}
%\newcommand{\pone}{\textbf{p}_1}
%\newcommand{\ltwo}{\textbf{l}_2}
%\newcommand{\ptwo}{\textbf{p}_2}
%\newcommand{\pthree}{\textbf{p}_3}
%\newcommand{\given}{\,|\,}
\newcommand{\g}{\,|\,}
\newcommand{\maxit}{\textcompute{maxit}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argsup}{\operatornamewithlimits{argsup}}
\newcommand*\DNA{\textsc{dna}}
\newcommand*\Let[2]{\State #1 $\gets$ #2}
\renewcommand{\bibname}{References}

@@

It is known (e.g.\ \citealt{henn&hodges:2014}) that $\logRLss$
can have multiple maxima,
though the incidence of multiple maxima is unknown.  Multi-modal posterior distributions arise readily from conflict between the likelihood and prior;  \cite{Liu&Hodges:2003} explores an important such conflict in detail and \cite{wakefield:1998} gives a naturally-occurring example explored further in \cite{henn&hodges:2014}.  Multiple maxima in restricted likelihoods have received far less attention and any statement about their incidence would be speculation.  To our knowledge, two naturally-occurring cases have have been reported, in \cite{welham_thompson:2009} and \cite{reiss_etal:2014};  \cite{henn&hodges:2014} report an artificial case and give a recipe for manufacturing examples.

@@

\section{Satisfying the Desiderata}
\subsection{Partial Derivatives Determine Lines}
\label{subsec:lines}
The partial derivatives of $\logRLss$ can be calculated from (\ref{eq:sum}):
\begin{subequations}
\label{eq:partials}
\begin{equation}
\label{eq:drlds}
  \frac{\partial\logRLss}{\partial\sigssq}
  = -\frac{1}{2} \sum_j
        \left[ \frac{a_jc_j}{\abss} - \frac{a_j d_j}{(\abss)^2} \right]
        = -\frac{1}{2} \sum_j
           \frac{a_j \left( a_jc_j\sigssq + b_jc_j\sigesq  - d_j\right)}{(\abss)^2}\\
\end{equation}
and
\begin{equation}\label{eq:drlde}
  \frac{\partial\logRLss}{\partial\sigesq} =
    -\frac{1}{2} \sum_j \left[ \frac{b_jc_j}{\abss} - \frac{b_j d_j}{(\abss)^2} \right]
    = - \frac{1}{2} \sum_j \frac{b_j \left( a_jc_j\sigssq + b_jc_j\sigesq  - d_j\right)}{(\abss)^2}.
\end{equation}
\end{subequations}

@@

%\noindent\textbf{Proof}
%Let $p$ be an arbitrary point inside $B_1$, as illustrated in Figure~(\ref{fig:boundingbox2}), and define $L \equiv \logRL(p)$; we use $L$ as a lower bound on $\logRL(\sshat)$.  The proof considers several regions outside $B$ in turn, as exemplified by the points $q_1$, $q_2$, $q_3$, and $q_4$ in Figure~\ref{fig:boundingbox2}.  Let $\widetilde{q_1} = (0,\widetilde{\sigma_s^2})$ be the intercept of $B$ and the $\sigssq$ axis and let $\widetilde{q_2} = (\sigma_e^{2*},\widetilde{\sigma_s^2})$.  Let $q_1 = (\sigesq{}_1, \sigssq{}_1)$ be a point satisfying $\sigesq{}_1 \le \sigma_e^{2*}$ and $\sigssq{}_1 \ge \widetilde{\sigma_s^2}$ --- above $B$ and to the left of the $s_z+1$ line.  The partial derivatives (\ref{eq:drlds}), between $q_1$ and $\widetilde{q_1}$ are negative for $j \in \{1, \dots, s_z, s_z+2\}$ but zero for $j=s_z+1$.  The partial derivatives (\ref{eq:drlde}), betweem $q_1$ and $\widetilde{q_2}$ are negative for $j \in \{1, \dots, s_z, s_z+1\}$ but nonnegative for $j=s_z+2$.  Let $\logRL_j(\cdot)$ denote the $j$'th term of \eqref{eq:sum} evaluated at $(\cdot)$.  
%\begin{equation}
%	\logRL(\sshat) - \logRL(q_1) \ge L - \sum_{j \ne s_z+1} \logRL_j(\widetilde{q_1}) - \logRL_{s_z+1}(\widetilde{q_2}),
%\end{equation}
%which is larger than $M$ if
%\begin{equation}
%\label{eq:q1}
%  \begin{split}
%    \sum_{j \ne s_z+1} \logRL_j(\widetilde{q_1})
%      &< L - M - \logRL_{s_z+1}(\widetilde{q_2})\\
%      &= L - M + \frac{1}{2} \left[ c_{s_z+1}\log\sigma_e^{2*} + \frac{d_{s_z+1}}{\sigma_e^{2*}}\right].
%  \end{split}
%\end{equation}
%Examination of (\ref{eq:sum}) shows that for any fixed $\sigesq$, in particular for $\sigesq=0$, and for $j \ne s_z+1$,\\ $\lim_{\sigssq \rightarrow \infty} \logRL_j(\sigesq,\sigssq) = -\infty$.  Thus $\widetilde{\sigma_s^2}$ can be chosen large enough so that the summation on the l.h.s.~of \eqref{eq:q1} is less than the r.h.s.~of \eqref{eq:q1}, and  \textbf{D1} is satisfied.
%
%Let $q_2 = (\sigesq{}_2, \sigssq{}_2)$ satisfy $\sigesq{}_2 \ge \sigma_e^{2*}$ and $\sigssq{}_2 \ge \widetilde{\sigma_s^2}$ --- above $B$ and to the right of the $s_z+1$ line.  (Points $q_2$ and $q_3$ in Figure~(\ref{fig:boundingbox2}) both satisfy these criteria.)  The partial derivatives (\ref{eq:drlds}, \ref{eq:drlde}) evaluated at $q_2$ are nonpositive for $j \in \{1, \dots, s_z+2\}$; therefore, $\logRL(\sshat) - \logRL(q_2) \ge L - \logRL(\widetilde{q_2})$.  The latter expression is greater than $M$ iff $\logRL(\widetilde{q_2}) < L-M$.  But examination of (\ref{eq:sum}) shows that for any fixed $\sigesq$, $\lim_{\sigssq \rightarrow \infty} \logRLss = -\infty$ and therefore $\widetilde{\sigma_s^2}$ can be chosen large enough so that \textbf{D1} is satisfied.
%
%Let $\widetilde{q_3} = (\widetilde{\sigma_e^2}, \sigma_s^{2*})$ and let $q_3 = (\sigesq{}_3, \sigssq{}_3)$ satisfy $\sigesq{}_3 \ge \widetilde{\sigma_e^2}$ and $\sigssq{}_3 \ge \sigma_s^{2*}$.  The partial derivatives (\ref{eq:drlds}, \ref{eq:drlde}) evaluated at $q_3$ are nonpositive for $j \in \{1, \dots, s_{z+2}\}$; therefore, $\logRL(\sshat) - \logRL(q_3) \ge L - \logRL(\widetilde{q_3})$.  The latter expression is greater than $M$ iff $\logRL(\widetilde{q_3}) < L-M$.  But examination of (\ref{eq:sum}) shows that for any fixed $\sigssq$, $\lim_{\sigesq \rightarrow \infty} \logRLss = -\infty$ and therefore $\widetilde{\sigma_e^2}$ can be chosen large enough so that \textbf{D1} is satisfied.
%
%Let $\widetilde{q_4} = (\widetilde{\sigma_e^2},0)$ and let $q_4 = (\sigesq{}_4, \sigssq{}_4)$ satisfy $\sigssq{}_4 \le \sigma_s^{2*}$ and $\sigesq{}_4 \ge \widetilde{q_4}$.  The partial derivatives \eqref{eq:drlds} evaluated at $q_4$ are nonpositive for $j \in \{1, \dots, s_z+1\}$  but nonnegative for $j=s_z+2$.  The partial derivatives \eqref{eq:drlde} evaluated at $q_4$ are nonpositive for $j \in \{1, \dots, s_z, s_z+2\}$  but nonnegative for $j=s_z+1$. Therefore,
%\begin{equation*}
%	\logRL(\sshat) - \logRL(q_4) \ge L - \sum_{j \ne s_z+2} \logRL_j(\widetilde{q_4}) - \logRL_{s_z+2}(\widetilde{q_3})
%\end{equation*}
%which is larger than $M$ if
%\begin{equation}
%\label{eq:q4}
%  \begin{split}
%    \sum_{j \ne s_z+2} \logRL_j(\widetilde{q_4})
%      &< L - M - \logRL_{s_z+2}(\widetilde{q_3})\\
%      &= L - M + \frac{1}{2} \left[ c_{s_z+2}\log\sigma_s^{2*} + \frac{d_{s_z+2}}{\sigma_s^{2*}}\right].
%  \end{split}
%\end{equation}
%Examination of (\ref{eq:sum}) shows that for any fixed $\sigssq$, in particular for $\sigssq=0$, and for $j \ne s_z+2$,\\ $\lim_{\sigesq \rightarrow \infty} \logRL_j(\sigesq,\sigssq) = -\infty$.  Thus $\widetilde{\sigma_e^2}$ can be chosen large enough so that the summation on the l.h.s.~of \eqref{eq:q4} is less than the r.h.s.~of \eqref{eq:q4}, and  \textbf{D1} is satisfied.
%

@@

	\logRL(\sshat) - \logRL(q) \ge L - \sum_{j \ne s_z+1} \logRL_j(\widetilde{q_1}) - \logRL_{s_z+1}(\widetilde{q_2}).

@@

      \sum_{j \ne s_z+1} \logRL_j(\widetilde{q_1})

@@

	\logRL(\sshat) - \logRL(q) \ge L - \sum_{j \ne s_z+2} \logRL_j(\widetilde{q_4}) - \logRL_{s_z+2}(\widetilde{q_3})

@@

      \sum_{j \ne s_z+2} \logRL_j(\widetilde{q_4})

@@

For any box $b$ let $L^b_j = \inf_{p\in b} \logRL_j(p)$ and $U^b_j = \sup_{p\in b} \logRL_j(p)$.  We have just shown that $L^b_j$ and $U^b_j$ are easily computable by evaluating $\logRL_j$ at either two points (two corners for lines like $j=2,3$) or three points (two corners and one on the line for lines like $j=1$).
Armed with the $L^b_j$'s and $U^b_j$'s we can compute bounds on $\logRLss$ within $b$:
\begin{equation}
\label{eq:bounds}
	L^b \equiv \sum_j L^b_j \le \inf_{(\sigssq,\sigesq)\in b} \logRLss \le
	\sup_{(\sigssq,\sigesq)\in b} \logRLss \le \sum_j U^b_j \equiv U^b.
\end{equation}
Because $\logRL$ is continuous, $U^b - L^b \rightarrow 0$ as $b$ shrinks in both directions, thus satisfying desideratum \textbf{D2}.

@@

\begin{algorithm}
  \caption{Learn areas in $B$ where log $f$ is high to within $\epsilon$
    \label{alg:findf}}
  \begin{algorithmic}[1]
    \Function{findf}{$B, \epsilon, M$}
      \Let{$active$}{list containing only $B$}
      \Let{$inactive$}{empty list}
      \Let{$L$}{$-\infty$}
      \While{length of $active > 0$}
        \For{each element $b$ in $active$}
          \Let{$L^b, U^b$}{get bounds on log $f$ in $b$ \Comment{see section \ref{sec:boundsinboxes}}}
        \EndFor
          \Let{tmp}{max($L^b$)}
         \Let{$L$}{max($L$, tmp)}
        \For{each element $b$ in $active$}
          \If{$U^b - L^b < \epsilon \enspace \textrm{or} \enspace U^b < L - M$}
            \State move $b$ from $active$ to $inactive$
          \Else
            \Let{$b_1, b_2, b_3, b_4$}{split $b$ into 4 smaller boxes}
            \State remove $b$ from $active$
            \State add $b_1, b_2, b_3, b_4$ to $active$
          \EndIf
        \EndFor
      \EndWhile
      \State \Return $inactive$ 
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

@@

The column space of $Z$ shares no dimensions with the column space of $X$ so $s_z=30$ and, for our $\logRLorig$ analysis, there are 31 lines in all, as shown in Figure~\ref{fig:gmst-lines}.
\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{figs/gmst-lines.pdf}
	\caption{The 31 lines for the $\logRLorig$ analysis of
	              global mean surface temperatures.}
	\label{fig:gmst-lines}
\end{figure}
As usual, we use $B^0 = B_1$, the box determined by the largest intercepts of the 31 lines on the $\sigesq$ and $\sigssq$ axes.
%and the control constants 
%\begin{equation*}
%	\maxit=\infty; \hspace{1cm} \epsilon=1; \hspace{1cm}
%	\delta_e= \delta_s=0; \hspace{1cm} M=7.
%\end{equation*}
After 25 iterations and about 35 minutes of computing time, all boxes became inactive.  Output is in Table~\ref{table:gmst_output}; boxes are displayed in Figure~\ref{fig:gmst1}.
\begin{table}[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Iteration & $n$ active boxes & $n$ inactive boxes & $L$\\
1 & 4 & 0 & $-\infty$\\
2 & 16 & 0 & -560.82\\
3 & 48 & 4 & -519.98\\
4 & 84 & 31 & -480.58\\
5 & 152 & 77 & -446.67\\
6 & 184 & 183 & -419.47\\
7 & 176 & 323 & -406.31\\
8 & 164 & 458 & -395.36\\
9 & 284 & 551 & -390.24\\
10 & 496 & 711 & -385.84\\
11 & 984 & 961 & -382.45\\
12 & 1792 & 1497 & -379.65\\
13 & 2880 & 2569 & -377.36\\
14 & 4668 & 4282 & -375.37\\
15 & 7312 & 7122 & -373.66\\
16 & 10336 & 11850 & -372.29\\
17 & 10108 & 19659 & -371.21\\
18 & 18596 & 25118 & -370.82\\
19 & 62488 & 28092 & -370.82\\
20 & 124240 & 59520 & -370.70\\
21 & 287596 & 111861 & -370.70\\
22 & 494292 & 275884 & -370.70\\
23 & 646808 & 608474 & -370.70\\
24 & 291944 & 1182296 & -370.70\\
25 & 0 & 1474240 & -370.70\\
\hline
\end{tabular}
\caption{The state of the algorithm after each of 25 iterations for the GMST data.}
\label{table:gmst_output}
\end{table}

>>>>

\renewcommand\thesection{\arabic{section}}
\usepackage{xspace}
\newcommand{\textcompute}{\textsf}
\newcommand{\N}{\text{N}} % Normal 
\newcommand{\R}{\textcompute{R}\xspace}
\newcommand{\IG}{\text{InvGam}}
\newcommand{\RL}{f}
\newcommand{\RLorig}{\text{RL}}
\newcommand{\logRL}{\log\RL}
\newcommand{\logRLorig}{\log\RLorig}
\newcommand{\sigssq}{\sigma_s^2}
\newcommand{\sigesq}{\sigma_e^2}
\newcommand{\sshat}{\hat\sigma^2_e,\hat\sigma^2_s}
\newcommand{\logRLss}{\logRL(\sigesq,\sigssq)}
\newcommand{\logRLssorig}{\logRLorig(\sigesq,\sigssq)}
\newcommand{\ass}{a_j\sigssq + \sigesq}
\newcommand{\abss}{a_j\sigssq + b_j\sigesq}
\newcommand{\fss}{f(\sigesq,\sigssq)\,}
%\newcommand{\mrle}{MRLE}
\newcommand{\mrle}{$\argsup\log f$}
%\newcommand{\lone}{\textbf{l}_1}
%\newcommand{\pone}{\textbf{p}_1}
%\newcommand{\ltwo}{\textbf{l}_2}
%\newcommand{\ptwo}{\textbf{p}_2}
%\newcommand{\pthree}{\textbf{p}_3}
%\newcommand{\given}{\,|\,}
\newcommand{\g}{\,|\,}
\newcommand{\maxit}{\textcompute{maxit}}
\newcommand{\argmax}{\operatornamewithlimits{argmax}}
\newcommand{\argsup}{\operatornamewithlimits{argsup}}
\newcommand*\DNA{\textsc{dna}}
\newcommand*\Let[2]{\State #1 $\gets$ #2}
\renewcommand{\bibname}{References}
\linespread{1.6}

@@

It is known (e.g.\ \citealt{henn&hodges:2014}) that $\logRLss$
can have multiple maxima,
though the incidence of multiple maxima is unknown.  Multi-modal posterior distributions arise readily from conflict between the likelihood and prior;  \cite{Liu&Hodges:2003} explores an important such conflict in detail and \cite{wakefield:1998} gives a naturally-occurring example explored further in \cite{henn&hodges:2014}.  Multiple maxima in restricted likelihoods have received far less attention and any statement about their incidence would be speculation.  To our knowledge, two naturally-occurring cases have been reported, in \cite{welham_thompson:2009} and \cite{reiss_etal:2014};  \cite{henn&hodges:2014} report an artificial case and give a recipe for manufacturing examples.

@@

\section{Satisfying the Desiderata}
\subsection{Partial Derivatives Determine Lines}
\label{subsec:lines}
The partial derivatives of $\logRLss$ can be calculated from (\ref{eq:sum}):
\begin{subequations}
\label{eq:partials}
\begin{equation}
\label{eq:drlds}
  \frac{\partial\logRLss}{\partial\sigssq}
  = -\frac{1}{2} \sum_{j=1}^{s_z+2}
        \left[ \frac{a_jc_j}{\abss} - \frac{a_j d_j}{(\abss)^2} \right]
        = -\frac{1}{2} \sum_{j=1}^{s_z+2}
            \frac{a_j \left( a_jc_j\sigssq + b_jc_j\sigesq  - d_j\right)}{(\abss)^2}\\
\end{equation}
and
\begin{equation}\label{eq:drlde}
  \frac{\partial\logRLss}{\partial\sigesq} =
    -\frac{1}{2} \sum_{j=1}^{s_z+2} \left[ \frac{b_jc_j}{\abss} - \frac{b_j d_j}{(\abss)^2} \right]
    = - \frac{1}{2} \sum_{j=1}^{s_z+2}
         \frac{b_j \left( a_jc_j\sigssq + b_jc_j\sigesq  - d_j\right)}{(\abss)^2}.
\end{equation}
\end{subequations}

@@

@@

	\logRL(\sshat) - \logRL(q) \ge L -
	  \sum_{\substack{j=1\\ j \ne s_z+1}}^{s_z+2} \logRL_j(\widetilde{q_1}) - \logRL_{s_z+1}(\widetilde{q_2}).

@@

      \sum_{\substack{j=1\\ j \ne s_z+1}}^{s_z+2} \logRL_j(\widetilde{q_1})

@@

	\logRL(\sshat) - \logRL(q) \ge L - \sum_{j=1}^{s_z+1} \logRL_j(\widetilde{q_4}) - \logRL_{s_z+2}(\widetilde{q_3})

@@

      \sum_{j=1}^{s_z+1} \logRL_j(\widetilde{q_4})

@@

For any box $b$ let $L^b_j = \inf_{p\in b} \logRL_j(p)$ and $U^b_j = \sup_{p\in b} \logRL_j(p)$.  We have just shown that $L^b_j$ and $U^b_j$ are easily computable by evaluating $\logRL_j$ at either two points (two corners for lines like $j=2,3$) or three points (two corners and one on the line for lines like $j=1$).
Armed with the $L^b_j$'s and $U^b_j$'s we can compute bounds on $\logRLss$ within $b$:
\begin{equation}
\label{eq:bounds}
	L^b \equiv \sum_{j=1}^{s_z+2} L^b \le \inf_{(\sigssq,\sigesq)\in b} \logRLss \le
	\sup_{(\sigssq,\sigesq)\in b} \logRLss \le \sum_{j=1}^{s_z+2} U^b_j \equiv U^b.
\end{equation}
Because $\logRL$ is continuous, $U^b - L^b \rightarrow 0$ as $b$ shrinks in both directions, thus satisfying desideratum \textbf{D2}.

@@

@@

\begin{algorithm}[H]
  \caption{Learn areas in $B$ where log $f$ is high to within $\epsilon$
    \label{alg:findf}}
  \begin{algorithmic}[1]
    \Function{findf}{$B, \epsilon, M$}
      \Let{$active$}{list containing only $B$}
      \Let{$inactive$}{empty list}
      \Let{$L$}{$-\infty$}
      \While{length of $active > 0$}
        \For{each element $b$ in $active$}
          \Let{$L^b, U^b$}{get bounds on log $f$ in $b$ \Comment{see section \ref{sec:boundsinboxes}}}
        \EndFor
          \Let{tmp}{max($L^b$)}
         \Let{$L$}{max($L$, tmp)}
        \For{each element $b$ in $active$}
          \If{$U^b - L^b < \epsilon \enspace \textrm{or} \enspace U^b < L - M$}
            \State move $b$ from $active$ to $inactive$
          \Else
            \Let{$b_1, b_2, b_3, b_4$}{split $b$ into 4 smaller boxes}
            \State remove $b$ from $active$
            \State add $b_1, b_2, b_3, b_4$ to $active$
          \EndIf
        \EndFor
      \EndWhile
      \State \Return $inactive$ 
    \EndFunction
  \end{algorithmic}
\end{algorithm}

@@

The column space of $Z$ shares no dimensions with the column space of $X$ so $s_z=30$ and, for our $\logRLorig$ analysis, there are 31 lines in all, as shown in Figure~\ref{fig:gmst-lines}.
\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{figs/gmst-lines.pdf}
	\caption{The 31 lines for the $\logRLorig$ analysis of
	              global mean surface temperatures.}
	\label{fig:gmst-lines}
\end{figure}
As usual, we use $B^0 = B_1$, the box determined by the largest intercepts of the 31 lines on the $\sigesq$ and $\sigssq$ axes.
%and the control constants 
%\begin{equation*}
%	\maxit=\infty; \hspace{1cm} \epsilon=1; \hspace{1cm}
%	\delta_e= \delta_s=0; \hspace{1cm} M=7.
%\end{equation*}
After 25 iterations and about 35 minutes of computing time, all boxes became inactive.  Output is in Table~\ref{table:gmst_output}; boxes are displayed in Figure~\ref{fig:gmst1}.
\begin{table}%[H]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Iteration & $n$ active boxes & $n$ inactive boxes & $L$\\
1 & 4 & 0 & $-\infty$\\
2 & 16 & 0 & -560.82\\
3 & 48 & 4 & -519.98\\
4 & 84 & 31 & -480.58\\
5 & 152 & 77 & -446.67\\
6 & 184 & 183 & -419.47\\
7 & 176 & 323 & -406.31\\
8 & 164 & 458 & -395.36\\
9 & 284 & 551 & -390.24\\
10 & 496 & 711 & -385.84\\
11 & 984 & 961 & -382.45\\
12 & 1792 & 1497 & -379.65\\
13 & 2880 & 2569 & -377.36\\
14 & 4668 & 4282 & -375.37\\
15 & 7312 & 7122 & -373.66\\
16 & 10336 & 11850 & -372.29\\
17 & 10108 & 19659 & -371.21\\
18 & 18596 & 25118 & -370.82\\
19 & 62488 & 28092 & -370.82\\
20 & 124240 & 59520 & -370.70\\
21 & 287596 & 111861 & -370.70\\
22 & 494292 & 275884 & -370.70\\
23 & 646808 & 608474 & -370.70\\
24 & 291944 & 1182296 & -370.70\\
25 & 0 & 1474240 & -370.70\\
\hline
\end{tabular}
\caption{The state of the algorithm after each of 25 iterations for the GMST data.}
\label{table:gmst_output}
\end{table}
